Type Flattening Obfuscation

### 2020-01-30 paper/tool.tex
add option for lightweight obfuscation

It may worth to note that the \emph{type flattening} is given by \emph{uCc}, not by the source code
complexity of tested functions. Indeed if they are compiled by, \emph{clang} or \emph{gcc} for example,
then their signatures are reconstructed precisely
by the decompilers. Last but not least, \emph{uCc} makes no effort in making disassembling or function
boundary detection hard: functions in tested binaries are perfectly detectable,
disassemblable and decompilable.

>>>>

It may worth to note that the \emph{type flattening} is given by \emph{uCc}, not by the source code
complexity of tested functions. Indeed if they are compiled by, \emph{clang} or \emph{gcc} for example,
then their signatures are reconstructed precisely
by the decompilers. Last but not least, \emph{uCc} attacks directly on type reconstruction algorithms,
it does not use obfuscation tricks
% , for example making disassembling or function boundary detection hard,
which make side effects on type
reconstruction: functions in tested binaries are perfectly detectable, disassemblable and
decompilable.
